A Comparative Ecophysiological Survey of Lycophytes, Ferns, and Seed Plants

### 2018-11-12 manuscript/manuscript.Rmd
added new plots for manuscript

To generate comparative physiological data, we followed two procedures. The first was to generate a series of detailed light response curves for a select number of species. The second approach, to increase our comparative sample size, was to make several survey measurements of maximum photosynthetic and conductance rates for additional species; this step was only completed at the Huyck Preserve. All gas exchange parameters were generated using the LiCor 6400 XT Photosynthesis System (Lincoln, NE). For the light response curves, the system was set up to a flow rate of 300 units, and a CO2 concentration of 400 umol m-2 s-1. Initial light measurements were made using the built-in quantum sensor to determine typical ambient light levels. These measurements were used to generate light response curves using appropriate light levels for high-light and low-light species separately. The light levels were not identical for each species, with several points being added or subtracted with each run, but they generally followed the same template. For high light species this was light levels of 1500, 1000, 800, 600, 500, 400, 300, 250, 200, 150, 100, 50, 25, 15, 10,5 and 0 (umol m-2 s-1) . Low light curves followed this pattern; 500, 400, 350, 300, 250, 200, 150, 100, 50, 25, 15, 10, 5 and 0 (again umol m-2 s-1). Using the data we generated from the light response curves, we developed an understanding of the levels at which low-light and high-light species reached their maximum photosynthetic rates. These data were then used to complete our survey measurements. All high-light species reached maximum rates at 1200 umol m-2 s-1 and all low-light species reached maximum rates at 600. All other LiCor parameters were identical to those used for the light response curves.

@@

Air-dried and pulverized tissues from each sample were analyzed for total C and N. Data for percent carbon and percent nitrogen were generated using a costech elemental analyzer blksjdf;jas. Phosphorus data were gathered using alsdjfsklj;

>>>>

To generate comparative physiological data, we followed two procedures. The first was to generate a series of detailed light response curves for a select number of species. The second approach, to increase our comparative sample size, was to make several survey measurements of maximum photosynthetic and conductance rates for additional species; this step was only completed at the Huyck Preserve. All gas exchange parameters were generated using the LiCor 6400 XT Photosynthesis System (Lincoln, NE). For the light response curves, the system was set up to a flow rate of 300 units, and a CO~2~ concentration of 400 umol m^-2 s^-1. Initial light measurements were made using the built-in quantum sensor to determine typical ambient light levels. These measurements were used to generate light response curves using appropriate light levels for high-light and low-light species separately. The light levels were not identical for each species, with several points being added or subtracted with each run, but they generally followed the same template. For high light species this was light levels of 1500, 1000, 800, 600, 500, 400, 300, 250, 200, 150, 100, 50, 25, 15, 10,5 and 0 (umol m-2 s-1). Low light curves followed this pattern; 500, 400, 350, 300, 250, 200, 150, 100, 50, 25, 15, 10, 5 and 0 (again umol m-2 s-1). Using the data we generated from the light response curves, we developed an understanding of the levels at which low-light and high-light species reached their maximum photosynthetic rates. These data were then used to complete our light saturated gas exchange survey measurements. All high-light species reached maximum rates at 1200 umol m-2 s-1 and all low-light species reached maximum rates at 600. All cuvette parameters were identical to those used for the light response curves.

@@

Air-dried and ground tissues from each leaf sample used for gas exchange were analyzed for total C and N. Foliar carbon and nitrogen content were generated using a costech elemental analyzer (machine). Phosphorus data were gathered using some digest (method)

## Stomatal anatomy
